Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-02 main.tex
to dos in red
add figures for first layer impulse response
add text to introduction

% imports
\usepackage[acronym,toc,shortcuts,nonumberlist]{glossaries}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{xcolor}

@@

\section{Introduction}
\draft{
Why is raw waveform modeling interesting?

\wvtwo is very successful and uses neural \fe.

Comparable to other neural feature extraction methods, but not closely studied in the literature.
Maybe some references or name some works which are similar.

@@

@@

\section{To Dos/Questions}
\begin{itemize}
  \item \wvtwo feature extractor vs. feature encoder
\end{itemize}

>>>>

% imports
\usepackage[acronym,toc,shortcuts,nonumberlist]{glossaries}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xcolor}

@@

\section{Introduction}
\glspl{AM} for \gls{ASR} traditionally makes use of hand-designed feature extraction methods like log Mel filterbank features \addref or Gammatone features \cite{schlueter:icassp07}.
These techniques are motivated by insights into the properties of the human auditory system.
However, their fixed design inevitably leads to information loss during the feature extraction.

This issue can be addressed by neural \fes.
Since their parameters are learned during training, these \fes can adapt to the need of \glspl{AM} and the loss of particularly helpful information may be avoided.
A number of works have been proposed in this direction, often using convolutional \glspl{NN} \addref but also applying parametrized functions \cite{ravanelli2018sincnet} and other architectures \cite{sainath2015cldnn}.

Recently, the \wvtwo framework \cite{facebook2020wav2vec2} has received large attention.
It is mainly known for its contrastive self-supervised pre-training, which allows to pre-train a model on large amounts of unlabeled audio data.
Subsequently, it can be fine-tuned for a specific downstream task at hand.
While the context network with multiple \transformer blocks constitutes the major part of the architecture, the \wvtwo model also makes use of a convolutional feature encoder.
\TODO{feature encoder vs. \fe here.}

While the \wvtwo \fe is similar to other neural feature extraction methods, it is not yet closely studied in the literature.
Choi et al. study the feature encoder\footnote{K. Choi and E. J. Yeo, “Opening the black box of wav2vec feature encoder,” arXiv preprint arXiv:2210.15386, 2022.}.%\cite{choi2022w2v2fe}

\draft{
Comparable to other neural feature extraction methods, but not closely studied in the literature.
Maybe some references or name some works which are similar.

@@

\subsection{Frequency Response of Learned Filters}
\input{figures/first_layer}

@@

{
\color{red}
\section{To Dos/Questions}
\begin{itemize}
  \item \wvtwo feature extractor vs. feature encoder
\end{itemize}
}
